\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-24 tex/ms.tex
added all figs

@@

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/phases.pdf}
    \caption{\label{fig:phases}
             \tess view of Sol d on every date in Sectors 1
             and 2 that was included in the regression. Each image is
             labeled with the corresponding timestamp in TJD.
             \codelink{EarthView}
             }
    \end{centering}
\end{figure}

@@

>>>>

\begin{figure}[ht!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/phases.pdf}
    \caption{\label{fig:phases}
             \tess view of Sol d on every date in Sectors 1
             and 2 that was included in the regression. Each image is
             labeled with the corresponding timestamp in TJD. 
             \codelink{EarthView}
             }
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/data.pdf}
    \caption{\label{fig:data}
             Normalized background flux in each of ten postage stamps
             for each of Sectors 1 and 2. Cadences where Sol d was
             below or very close to the edge of the sunshade were masked.
             While the planet is in view for the majority of both orbits
             in Sector 1, it is only visible in the data at the very end
             of each orbit in Sector 2.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/starry_model.pdf}
    \caption{\label{fig:starry_model}
             Normalized surface reflectance versus time for the maximum
             likelihood \starry model in each of the four orbits of \tess
             in Sectors 1 and 2.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/model.pdf}
    \caption{\label{fig:model}
             \emph{Top:} Median flux across all postage stamps (black) and
             the median maximum likelihood model (blue) across Sectors 1 and 2.
             \emph{Bottom:} Median residuals about the maximum likelihood fit.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map.pdf}
    \caption{\label{fig:map}
             \emph{Top:} The maximum likelihood model for the surface albedo
             of Sol d, weighted by the visibility across Sectors 1 and 2. The
             dashed white lines indicate latitudes above/below which the
             visibility drops below 50\%. Black contours indicate coastlines
             derived from current state-of-the-art models of the surface geography 
             of Sol d.
             \emph{Bottom:} Actual corrected surface reflectance in the red band of the
             \emph{VIIRS} imager, averaged over the same date range and weighted
             by the same visibility function. This bandpass covers only about one
             quarter of the \tess bandpass, so deviations between the two images
             are to be expected.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}

The bottom panel of Figure~\ref{fig:map} shows the corrected surface
reflectance obtained from the
Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite. The 
image shows the corrected surface reflectance in the I1 band of the instrument,
averaged over the 28 days of data analyzed in this work, and weighted by the
\tess visibility as in the top panel.
The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$
\footnote{\url{http://rammb.cira.colostate.edu/projects/npp/VIIRS_bands_and_bandwidths.pdf}},
and therefore covers only about one-fourth of the bandpass of \tess
(nominally 0.6 - 1.0 $\mu\mathrm{m}$).
